\blogsubsubsection{sssec:ex1_161_17}{C-1.16 \& C-1.17}{chap:PythonPrimer}{} \label{sssec:ex1_161_17}

In our implementation of the scale function (page 25), the body of the loop executes the command \texttt{data[j] *= factor}. We have discussed that numeric types are immutable, and that use of the \texttt{*=} operator in this context causes the creation of a new instance (not the mutation of an existing instance).
How is it still possible, then, that our implementation of scale changes the actual parameter sent by the caller?

Had we implemented the scale function (page 25) as follows, does it work properly?

\begin{lstlisting}[title=The incorrect\_way]
def scale(data, factor):
	for val in data:
		val *= factor
\end{lstlisting}

Explain why or why not.

Well... here are some inmutable types in Python.

\begin{itemize}
	\item numerical types
	\item string types
	\item types
\end{itemize}

And here are some mutable types.

\begin{itemize}
	\item lists
	\item dicts
	\item classes
\end{itemize}

So taken by that premise, if we want a function that modifies numeric values in place, we would need a \texttt{class} that wraps that numeric value. This is not trivial. So we are going to take respectfully a class done by The Edwards Research group (\url{http://www.edwards-research.com/}), this class is presented here: \url{http://blog.edwards-research.com/2013/09/mutable-numeric-types-in-python/}.

It is everything you dreamed of, I give you, a mutable numeric. 

\lstinputlisting[title=Mutable Numeric]{../../GoodrichTamassiaGoldwasser/ch01/MutableNum.py}

Now onto the second question... if numeric types are not valid then of course that method is not going to work. You would need to do something \textbf{radical} like returning a \textbf{new list}. As follows:

\begin{lstlisting}[title=Returning new\_list]
def scale(data, factor):
    return [x*factor for x in data]
\end{lstlisting}

We can also change the list number by replacing the value in the list, remember that lists are mutable, so we can change that, we just can't change the number.

\lstinputlisting[title=Exercise C-1.16 \& C-1.17]{../../GoodrichTamassiaGoldwasser/ch01/c116c117.py}

